---
title: "codeCRANG_SF_edits"
author: "Stephen Formel"
date: "11/25/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, 
                      message = FALSE, 
                      warning = FALSE)
```

```{r load libraries, }

library(knitr)
library(kableExtra)
library(tidyverse)
library(readxl)
library(data.table)
library(lubridate)
library(magrittr)
library(scales)
library(reshape2)
library(stringr)
library(stringi)
library(cowplot)

```


## What it is and what it isn't

- Import datasets as a list
- remove columns we don't need 
- make variables to separate out:
  - datasets
  - channels
  - incubation periods
- Make summary descriptive stats
  - Do linear regression and get stats on each
  - dataset x channel x incubation
  
```{r }

#make list of files
FL <- list.files(path = "./", pattern = "*DO.csv",
                 full.names = TRUE, 
                 all.files = FALSE)

#make dataset name variable
set_name <- str_extract(FL, pattern = "\\d{4}DO")


#Keep this in here as a note to how we might deal with the data when it gets corrupted

#strip non-ASCII characters
# O2.list <- lapply(FL, read.table, 
#                   sep = "\t",
#                   skip = 21,
#                   strip.white = TRUE,
#                   header = TRUE,
#                   fileEncoding="Latin-1")
# 
# function(x) stri_trans_general, "latin-ascii")

#read in data into list

O2.list <- lapply(FL, read.table, 
                  sep = "\t",
                  skip = 21,
                  strip.white = TRUE,
                  header = TRUE,
                  fileEncoding="UTF-16")

#remove empty columns
O2.list <- lapply(O2.list, function(x){
  x <- Filter(function(y)!all(is.na(y)), x)
         })

#Remove Temp C column as it seems to match the temp of all channels, except Channel 2.  Not sure why that one is different, but it is.

O2.list <- lapply(O2.list, function(x) {
  x %>% select(-Temperature...C.)
}) 

#gather into channels
O2.list <- lapply(O2.list, function(x) {
  gather(x, key = "Variable", value = "Value", Oxygen.CH.1:Temperature.CH.4)
})

#split Variable string for Channel info - from reshape2 pkg
O2.list <- lapply(O2.list, function(x) {
  y <- colsplit(x$Variable,"\\.",c("Variable","Channel"))
  x$Variable <- y$Variable
  x$Channel <- y$Channel
  return(x)
})

#spread
O2.list <- lapply(O2.list, function(x) {
  spread(x, key = Variable, value = Value)
})

#make time column
O2.list <- lapply(O2.list, function(x) {
  x$date_time <- as.POSIXct(strptime(paste(x$Date..DD.MM.YYYY., 
                            x$Time..HH.MM.SS.), 
                      format =  "%m/%d/%Y %I:%M:%S %p"), tz = "UTC")
  return(x)
})

#Add Dataset name variable
O2.list <- Map(cbind, O2.list, data_name = set_name)

O2 <- rbindlist(O2.list) %>% 
  arrange(Channel, date_time)

```


```{r, out.width = "100%"}

# Split by Incubation Reference Times
#This file is made by hand and contains the start/stop time of each incubation.

#Read reference file and split into incubation subsets

IR_name <- list.files(path = "./", pattern = "IncRef*.*csv")
IncReference <- read.csv(IR_name,header=TRUE)

IncReference$Start <- as.POSIXct(IncReference$Start, tz = "UTC")
IncReference$Stop <- as.POSIXct(IncReference$Stop, tz = "UTC")

#may need to adjust to be inclusiv for bounds
overlap.function <- function(vals) {
  rowSums(mapply(function(a,b) between(vals, a, b),
                 IncReference$Start, IncReference$Stop)) > 0
}


O2 <- O2 %>%
  filter(overlap.function(O2$date_time))

#It appears as if Incubations 6-8 might have incorrect times

O2$Set <- ifelse(between(O2$date_time, 
                    lower = IncReference$Start[1], 
                    upper =  IncReference$Stop[1]),
                 yes = 1,
                 no = ifelse(between(O2$date_time, 
                    lower = IncReference$Start[2], 
                    upper =  IncReference$Stop[2]),
                 yes = 2,
                 no = ifelse(between(O2$date_time, 
                    lower = IncReference$Start[3], 
                    upper =  IncReference$Stop[3]),
                 yes = 3,
                 no = ifelse(between(O2$date_time, 
                    lower = IncReference$Start[4], 
                    upper =  IncReference$Stop[4]),
                 yes = 4,
                 no = ifelse(between(O2$date_time, 
                    lower = IncReference$Start[5], 
                    upper =  IncReference$Stop[5]),
                 yes = 5,
                 no = ifelse(between(O2$date_time, 
                    lower = IncReference$Start[6], 
                    upper =  IncReference$Stop[6]),
                 yes = 6,
                 no = ifelse(between(O2$date_time, 
                    lower = IncReference$Start[7], 
                    upper =  IncReference$Stop[7]),
                 yes = 7,
                 no = ifelse(between(O2$date_time, 
                    lower = IncReference$Start[8], 
                    upper =  IncReference$Stop[8]),
                 yes = 8,
                 no = NA)))))))) %>% 
  as.factor()

#Make Relative Time by Set
O2 <- O2 %>% 
  group_by(Set, Channel) %>% 
  mutate(Rel_Time = row_number()/2)

#Just to clean up plot and show Nate
# O2$Channel <- plyr::revalue(O2$Channel, replace = c("CH.1" = "CH5",
#                                                     "CH.1.2" = "CH1",
#                                                     "CH.2.2" = "CH2",
#                                                     "CH.3.2" = "CH3",
#                                                     "CH.4.2" = "CH4"))
# #Just to clean up plot and show Nate
# O2$Set <- plyr::revalue(O2$Set, replace = c("1" = "Incubation 1",
#                                                     "2" = "Incubation 2",
#                                                     "3" = "Incubation 3",
#                                                     "4" = "Incubation 4",
#                                                     "5" = "Incubation 5"))


#normal plot
O2 %>%
ggplot(aes(x = Rel_Time,
           y = Oxygen,
           fill = Set)) +
  geom_point(shape = 21,
             alpha = 0.5) +
  facet_grid(cols = vars(Channel),
             rows = vars(data_name)) +
  geom_smooth(method = "lm",
              color = "black", size = 0.5) +
  #scale_x_datetime(labels = date_format("%D \n %H:%M")) + 
  theme_bw() +
  theme(legend.position = "right",
        axis.text.x = element_text(angle = 45, hjust = 1),
        panel.spacing = unit(2, "lines")) +
  labs(x = "Minutes",
       fill = "Incubation")

ggsave(filename = "./figures/test_plot.png", width = 5, height = 3, units = "in")


```

### Stats

You might want to think about a GLM for this to control for the random effect of Sensor and/or tank.  

```{r }

# summary_stats <- function(x, cat_var, num_var){
#   cat_var <- enquo(cat_var)
#   num_var <- enquo(num_var)
# 
#   x %>%
#     group_by(!!cat_var) %>%
#     summarize(avg = mean(!!num_var), 
#               n = n(), 
#               sd = sd(!!num_var), 
#               se = sd/sqrt(n),
#               min = min(!!num_var),
#               max = max(!!num_var))
# }

# sum_fun <- function(.data, .summary_var, .group_vars) {
#   summary_var <- enquo(.summary_var)
# 
#   .data %>%
#     group_by_at(.group_vars) %>%
#     summarise(mean = mean(!!summary_var))
# }

# sum.stats <- O2 %>% 
#   summary_stats(cat_var = vars(data_name, Channel, Set), num_var = Oxygen)


sum.stats <- O2 %>%
  na.omit() %>% 
    group_by(data_name, Channel, Set) %>%
    summarize(avg = mean(Oxygen), 
              n = n(), 
              sd = sd(Oxygen), 
              se = sd/sqrt(n),
              min = min(Oxygen),
              max = max(Oxygen))
 

lm.stats <-  O2 %>%
  na.omit() %>% 
  group_by(data_name, Channel, Set) %>%
  do({
    result = lm(Oxygen ~ date_time, .)
    tibble(r_squared = 
                 result %>% 
                 summary %>% 
                 use_series(adj.r.squared),
               p_value = 
                 result %>% 
                 anova %>% 
                 use_series(`Pr(>F)`) %>% 
                 extract2(1) ) %>%
      bind_cols(
        result %>%
          coef %>%
          as.list %>%
          as_tibble) %>%
      select(-`(Intercept)`)})

#Combine stats

all.stats <- inner_join(x = sum.stats, y = lm.stats )

#convert seconds to minute
all.stats$date_time <- all.stats$date_time*60

#change name to "slope"
all.stats <- all.stats %>% 
  rename("slope per min" = date_time) 

#Arrange by incubation - needed for final table

all.stats <- all.stats %>% 
  arrange(Set)

#Change Set name
all.stats$Set <- plyr::revalue(all.stats$Set, replace = c("1" = "Incubation 1",
                                                    "2" = "Incubation 2",
                                                    "3" = "Incubation 3",
                                                    "4" = "Incubation 4",
                                                    "5" = "Incubation 5",
                                                    "6" = "Incubation 6",
                                                    "7" = "Incubation 7",
                                                    "8" = "Incubation 8"))


#view stats
all.stats %>% 
  #select(-Set) %>% 
  dplyr::mutate_if(is.numeric, funs(as.character(signif(., 3)))) %>%
    kable(., caption = "O2 Sumary Stats", booktabs = T) %>%
  kable_styling() %>% 
  pack_rows(index = table(all.stats$Set)) %>% 
  collapse_rows(columns = 1, valign = "top") %>% 
  remove_column(columns = 3)



```

End Script